Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-02-14 content.tex
EOD

Here we specify a different set of experiments: we
need to state that we already have an experiment for
the generative model, as well as that we want all the other inference models 
to compete. We call the competing models 'candidate models'.
As model selection is commonly performed on the full list of available 
candidate models, \verb;pirouette; has a dedicated function 
for this choice: \verb;create_all_experiments; creates a full set 
of 40 experiments, 
containing the inference models of all combinations of 4 nucleotide substitution model, 
2 clock models and 2 birth-death tree priors. All we need to add is to exclude the 
inference model in the generative experiment:

@@

\begin{lstlisting}[
  language = R, 
  floatplacement = ht, 
  frame = single, 
  label = {lst:combine_all_experiments},
  caption = {
    Create a collection of experiments, with 1
    generative model, and 39 candidate models.
  }
]
experiments <- c(
  list(generative_experiment),
  candidate_experiments
)
\end{lstlisting}

>>>>

Here we specify a different set of experiments: we
need to state that we already have an experiment for
the generative model, as well as that we want all the other inference models 
to compete. We call the competing models 'candidate models'.
As model selection is commonly performed on the full list of available 
candidate models, \verb;pirouette; has a dedicated function 
for this choice: \verb;create_all_bd_experiments; creates a full set 
of 16 experiments, 
containing the inference models of all combinations of 4 nucleotide substitution model, 
2 clock models and 2 birth-death tree priors. All we need to add is to exclude the 
inference model in the generative experiment:

@@

\begin{lstlisting}[
  language = R, 
  floatplacement = ht, 
  frame = single, 
  label = {lst:combine_all_experiments},
  caption = {
    Create a collection of experiments, with 1
    generative model, and 15 candidate models.
  }
]
experiments <- c(
  list(generative_experiment),
  candidate_experiments
)
\end{lstlisting}
